---
title: "McD_Nutrient_Menu - Linear Regression Model"
author: "Aravind"
date: "January 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

McDonalds nutrient menu is an interesting dataset that contain values of calories, fat,  cholesterol, carbohydrates, sodium content, protein, fiber and vitamins of different type of food served at McDonalds.
	 Dependent Variable(Target) = Calories
	 
Data Set Link : https://www.kaggle.com/mcdonalds/nutrition-facts/data
Rmd Code : http://www.instituteofanalytics.com/forum/discussion/18/an-example-of-multiple-regression-model#latest
	 
```{r}
data <- read.csv("menu.csv")
str(data)
```


we can do scatter plots and corrplots to check relation among variables
```{r}
require(lattice)
splom(~data[c(4,6,11,13,15,17,19,20)],groups = NULL, data = data, axis.line.tck = 0, axis.text.alpha = 0)
require(corrplot)
cr <- cor(data[c(4,6,11,13,15,17,19,20)])
corrplot(cr,method = "number")
```

Total fat has a high corelation = 0.9, followed by protein = 0.79 and carbohydrates = 0.78

Split the dataset into train and test
```{r}
library(caTools)
set.seed(2) #to get the same split everytime
split <- sample.split(data$Calories,SplitRatio = 0.70)
train <- subset(data,split == "TRUE")
test <- subset(data, split == "FALSE")
```

Let's first build a Linear regression model between calories and total fat.
Independent Variable - Total.Fat

Scatter plot and Conditional expectation(mean) plot
```{r}
require(dplyr)
#Scatter PLot
plot(train$Total.Fat,train$Calories,main = "Scatter Plot",xlab = "Total Fat", ylab = "Calories")
abline(lm(train$Calories~train$Total.Fat))
#Conditional Expectation Plot
dataexp <- summarise(group_by(train,Total.Fat),calmean = mean(Calories))
plot(dataexp$Total.Fat,dataexp$calmean,xlab = "Total Fat",ylab = "mean - calories",main = "Conditional 
     Expectation(mean) Plot")
```

Linear Regression Model
```{r}
model1 <- lm(Calories~Total.Fat,data = train)
summary(model1)
```


value of intercept = 151.838
value of slope = 15.180

Both the values are significant(*** refers to high signficance)
R-squared = 85% (This means 82% of variance in calories is explained by total fat)
The overall p-value is also significant

The linear equation to predict calories : Calories = 151.5882 + 15.2965*total fat



# Lets Build a multiple regression model.

From corplots we found out that total fat, protein and carbohydrates are highly corelated.

```{r}
model <- lm(Calories~ Total.Fat + Protein + Carbohydrates, data = train)
summary(model)
```

R - sq value of 1. These three variables almost explains 100% of variance in calories

#Regression Diagnostics
```{r}
plot(model, which = 1:4)
```

CD > = k/n (k is # of predictors, n is sample size)
CD > = 3/189 = 0.016
Rough cut off - 4/n = 4/189 = 0.02.
Observations 120,121,259 can be removed and model can be rebuilt.

```{r}
train <- train[-c(120,121,259),]
model <- lm(Calories~ Total.Fat + Protein + Carbohydrates, data = train)
summary(model)
```

# Predict
```{r}
predictions <- predict(model,test)
predictions
```
#Now, lets compare actual values and predicted values
```{r}
plot(test$Calories,type = "l",lty = 1.8, col="green")
lines(predictions,type = "l", col = "blue")
```

almost 100% accurate.(Lines overlap)

# Future Predictions
Say, for values of Total fat = 20, Protein = 18 & Carbohydatres = 33
```{r}
predict(model,data.frame(Total.Fat = 20,Protein = 18,Carbohydrates = 33))
```
We get, calories = 382.5207



